Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-19 article.Rmd
Use theme_few() from ggthemes

article_theme <- theme(legend.title = element_blank())

@@

leslie_plot <- leslie_df %>%
  ggplot(aes(x = year, y = prop_female)) +
  geom_smooth() + 
  geom_point() +
  ggtitle("Proportion of female uses of the name 'Leslie,' 1820-2012") +
  xlab(NULL) + ylab(NULL) + ylim(0, 1) +
  geom_hline(yintercept = 0.5) + 
  annotate("text", x = 1900, y = 0.45, label = "Male") +
  annotate("text", x = 1900, y = 0.55, label = "Female")

@@

selected_names_plot <- ssa_national %>%
  filter(name %in% plot_names) %>%
  mutate(prop_female = female / (female + male)) %>%
ggplot(aes(x = year, y = prop_female, color = name)) +
  geom_smooth(se = FALSE) +
  ggtitle("Changes in selected names, 1930-2012") +
  xlim(1930, 2012) + 
  xlab(NULL) + ylab(NULL) + ylim(0, 1) +
  geom_hline(yintercept = 0.5) +
  annotate("text", x = 1965, y = 0.45, label = "Male") +
  annotate("text", x = 1965, y = 0.55, label = "Female")

@@

```{r}
genderdata::ssa_national %>%
  group_by(year) %>%
  summarize(ratio = sum(female) /sum(female + male)) %>%
  ggplot(aes(x = year, y = ratio)) +
  geom_line() +
  ggtitle("Percentage of SSA dataset that is female") +
  xlab(NULL) + ylab(NULL)
```

>>>>

# I like 
article_theme <- theme(legend.title = element_blank()) + theme_few()

@@

leslie_plot <- leslie_df %>%
  ggplot(aes(x = year, y = prop_female)) +
  geom_smooth() + 
  geom_point() +
  ggtitle("Proportion of female uses of the name Leslie, 1820-2012") +
  xlab(NULL) + ylab(NULL) + ylim(0, 1) +
  geom_hline(yintercept = 0.5) + 
  annotate("text", x = 1900, y = 0.45, label = "Male") +
  annotate("text", x = 1900, y = 0.55, label = "Female") +
  article_theme

@@

selected_names_plot <- ssa_national %>%
  filter(name %in% plot_names) %>%
  mutate(prop_female = female / (female + male)) %>%
ggplot(aes(x = year, y = prop_female, color = name)) +
  geom_smooth(se = FALSE) +
  ggtitle("Changes in selected names, 1930-2012") +
  xlim(1930, 2012) + 
  xlab(NULL) + ylab(NULL) + ylim(0, 1) +
  geom_hline(yintercept = 0.5) +
  annotate("text", x = 1965, y = 0.45, label = "Male") +
  annotate("text", x = 1965, y = 0.55, label = "Female") +
  article_theme

@@

```{r}
genderdata::ssa_national %>%
  group_by(year) %>%
  summarize(ratio = sum(female) /sum(female + male)) %>%
  ggplot(aes(x = year, y = ratio)) +
  geom_line() +
  ggtitle("Percentage of SSA dataset that is female") +
  xlab(NULL) + ylab(NULL) +
  article_theme
```
